\documentclass[12pt]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{pifont}

% Allows for left, center, and right alligned text on the
% same line.
\newcommand\textline[4][t]{%
  \par\smallskip\noindent\parbox[#1]{.333\textwidth}{\raggedright\texttt#2}%
  \parbox[#1]{.333\textwidth}{\centering#3}%
  \parbox[#1]{.333\textwidth}{\raggedleft#4}\par\smallskip%
}

% Disables page numbering.
\pagenumbering{gobble}

\begin{document}

	\begin{center}
		\noindent \Large{\textbf{Liam Wynn}}\\
		\noindent \small{Portland, Oregon}
	\end{center}

	\begin{flushleft}
	\textline[t]{wynnliam@pdx.edu}{wynnliam.github.io}{503 747 9596}
	\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
	\end{flushleft}

	\noindent {\bf Qualifications} $\bullet$ Comfortable in a wide range of programming paradigms and languages. $\bullet$ Experienced writing thorough documentation on projects.  $\bullet$ Use math and theory to derive algorithms that I implement, test, and optimize. $\bullet$ Adept at learning new tools and technologies. $\bullet$ Thrive in both team and individual settings.

	% The * disables numbering.
	\section*{Education}
	\noindent {\bf Portland State University}\hfill Portland, Oregon \\
 	\noindent \emph {B.S., magna cum laude, Computer Science, Mathematics Minor} \hfill 2014 - 2019
	\begin{itemize}[noitemsep]
		\item GPA: 3.85
		\item Academic Honors: Dean's List (7 semesters).
		\item Inducted into Phi Kappa Phi National Honor Society 2018.
	\end{itemize}

	%--------------------------------------------------------------------------------------------
	\section*{Experience}
	\noindent {\bf Avantor Sciences}\hfill Hillsboro, Oregon\\
	\noindent \emph{Fabrication Support Specialist}\hfill November 2019 - Present
	\begin{itemize}[noitemsep]
		\item Operate technical equipment and computer systems to perform preventative maintenance.
		\item Coordinate team to handle deliver chemicals and materials to customers.
		\item Significantly reduced machine maintenance costs by creating accessible database of unused parts on shelves.
	\end{itemize}

	\noindent {\bf Standard Insurance Company}\hfill Portland, Oregon\\
	\noindent \emph{Software Development Intern}\hfill July 2018 - November 2018
	\begin{itemize}[noitemsep]
		\item Worked on the back end of web applications using Java and Springboot.
		\item  Did code reviews, unit testing, and agile/scrum software development.
		\item  Worked with several other teams to complete projects.
	\end{itemize}

	\noindent {\bf Portland State University}\hfill Portland, Oregon\\
	\noindent\emph{Computer Science Tutor}\hfill April 2016 - August 2019
	\begin{itemize}[noitemsep]
		\item Assisted lower division Computer Science students with their course work and development endeavors.
		\item  Helped students with problems that ranged from systems programming to rudimentary logic and discrete mathematics.
	\end{itemize}

	%--------------------------------------------------------------------------------------------

	\section*{Projects}
	\noindent {\bf VA Audiology Web App} - \emph{Typescript, Node.js, SQL} \\
	\noindent January 2019 - June 2019 \\
	\noindent For my senior capstone project, I worked with a team to add a back end to an existing application for the VA.
	This included a SQL database, a Node.js backend, and rewriting several parts of the existing front end to utilize the latter two systems.
	\noindent \\

	\noindent {\bf Raycore} - \emph{C} \\
	\noindent April 2018 - February 2020 \\
	\noindent A game engine built around ray casting which is a technique for rendering pseudo-3D environments. Rendering uses several numerical 
	approximations and low-level optimizations to improve runtime efficiency.\\

	\noindent {\bf Texture Generator} - \emph{Python, Tensorflow} \\
	\noindent November 2018 - Present\\
	\noindent Employed a variational autoencoder to generate texture images. Both the encoder network uses a convolution layers with leaky ReLU activation.
	The decoder uses transposed convolution layers with leaky ReLU activation. Uses the Adam Optimizer algorithm to train.
	\noindent \\

	% Should only be relevant to the job at hand.
	\section*{Technical Skills}
		\noindent {\bf Languages:} \normalsize{C, C++, C\#, Haskell, Python, Java, Javascript, SQL, x86-64 Assembly, Lisp}\\
		\noindent {\bf Libraries and Frameworks:}  \normalsize{STL, Tensorflow, NumPy, OpenGL, WebGL, SDL2, CUDA, three.js, socket.io, jQuery, Node.js, Express.js, React, Asyncio, Pyro4, SCOOP}\\
		\noindent {\bf Computer Skills:} \normalsize{GNU/Linux, Shell, Git Command Line, Vim, GDB, Valgrind, AWS, Docker, Latex, Google Cloud, Google AI Platform}\\

\end{document}
